Allocation Removal by Partial Evaluation in a Tracing JIT

### 2010-10-14 talk/pepm2011/paper.tex
give a unit
two things from samuele, regen pdf

Note how the functions that are called by \lstinline{f} are automatically inlined
into the trace. The method calls are always preceded by a \lstinline{guard_class}
operation, to check that the class of the receiver is the same as the one that
was observed during tracing.\footnote{\lstinline{guard_class} performs a precise
class check, not checking for subclasses.} These guards make the trace specific
to the situation where \lstinline{y} is really a \lstinline{BoxedInteger}, it can
already be said to be specialized for \lstinline{BoxedIntegers}. When the trace is
turned into machine code and then executed with \lstinline{BoxedFloats}, the
first \lstinline{guard_class} instruction will fail and execution will continue
using the interpreter.

@@

@@

\begin{figure*}
\begin{center}
\begin{tabular}{|l||r|r|r|r|}
\hline
	&Cpython	&Psyco	&PyPy w/o optimizations	&PyPy w/ optimizations \\
\hline
crypto\_pyaes	&2757.80 $\pm$ 0.98	&67.90 $\pm$ 0.47	&1652.00 $\pm$ 4.00 &266.86 $\pm$ 5.94 \\
django	&993.19 $\pm$ 0.50	&913.51 $\pm$ 4.22	&694.73 $\pm$ 2.86 &259.53 $\pm$ 1.79 \\
fannkuch	&1987.22 $\pm$ 2.02	&944.44 $\pm$ 0.61	&566.99 $\pm$ 1.06 &466.87 $\pm$ 1.85 \\
go	&947.21 $\pm$ 1.58	&445.96 $\pm$ 0.68	&2197.71 $\pm$ 25.21 &316.15 $\pm$ 9.33 \\
html5lib	&13987.12 $\pm$ 19.51	&17398.25 $\pm$ 36.50	&27194.45 $\pm$ 46.62	&10092.19 $\pm$ 23.50 \\
meteor-contest	&346.98 $\pm$ 0.35	&215.66 $\pm$ 0.23	&433.04 $\pm$ 1.45 &392.85 $\pm$ 0.87 \\
nbody\_modified	&637.90 $\pm$ 1.82	&256.78 $\pm$ 0.18	&135.55 $\pm$ 0.33 &103.93 $\pm$ 0.25 \\
pyflate-fast	&3169.35 $\pm$ 1.89	&1278.16 $\pm$ 3.13	&3285.89 $\pm$ 8.51	&1822.36 $\pm$ 11.52 \\
raytrace-simple	&2744.60 $\pm$ 51.72	&1072.66 $\pm$ 1.08	&2778.27 $\pm$ 15.13	&647.24 $\pm$ 5.44 \\
richards	&354.06 $\pm$ 1.00	&63.48 $\pm$ 0.15	&383.93 $\pm$ 3.28 &88.32 $\pm$ 0.91 \\
spambayes	&299.16 $\pm$ 0.35	&338.68 $\pm$ 3.14	&580.90 $\pm$ 24.68 &397.37 $\pm$ 10.60 \\
spectral-norm	&478.63 $\pm$ 0.80	&139.83 $\pm$ 1.54	&353.51 $\pm$ 1.39 &112.10 $\pm$ 1.17 \\
telco	&1207.67 $\pm$ 2.03	&730.00 $\pm$ 2.66	&1296.08 $\pm$ 4.37 &495.23 $\pm$ 2.14 \\
twisted\_names	&9.58 $\pm$ 0.01	&10.43 $\pm$ 0.01	&17.99 $\pm$ 0.27	&7.13 $\pm$ 0.09 \\
\hline
\end{tabular}
\end{center}
\caption{Benchmark Times}
\label{fig:times}
\end{figure*}

>>>>

The method calls in the trace are always preceded by a \lstinline{guard_class}
operation, to check that the class of the receiver is the same as the one that
was observed during tracing.\footnote{\lstinline{guard_class} performs a precise
class check, not checking for subclasses.} These guards make the trace specific
to the situation where \lstinline{y} is really a \lstinline{BoxedInteger}, it can
already be said to be specialized for \lstinline{BoxedIntegers}. When the trace is
turned into machine code and then executed with \lstinline{BoxedFloats}, the
first \lstinline{guard_class} instruction will fail and execution will continue
using the interpreter.

@@

XXX add a footnote saying that "static" is meant in the sense of PE, not static
allocation

@@

\begin{figure*}
\begin{center}
\begin{tabular}{|l||r|r|r|r|}
\hline
	&Cpython	&Psyco	&PyPy w/o optimizations	&PyPy w/ optimizations \\
\hline
crypto\_pyaes	&2757.80 $\pm$ 0.98	&67.90 $\pm$ 0.47	&1652.00 $\pm$ 4.00 &266.86 $\pm$ 5.94 \\
django	&993.19 $\pm$ 0.50	&913.51 $\pm$ 4.22	&694.73 $\pm$ 2.86 &259.53 $\pm$ 1.79 \\
fannkuch	&1987.22 $\pm$ 2.02	&944.44 $\pm$ 0.61	&566.99 $\pm$ 1.06 &466.87 $\pm$ 1.85 \\
go	&947.21 $\pm$ 1.58	&445.96 $\pm$ 0.68	&2197.71 $\pm$ 25.21 &316.15 $\pm$ 9.33 \\
html5lib	&13987.12 $\pm$ 19.51	&17398.25 $\pm$ 36.50	&27194.45 $\pm$ 46.62	&10092.19 $\pm$ 23.50 \\
meteor-contest	&346.98 $\pm$ 0.35	&215.66 $\pm$ 0.23	&433.04 $\pm$ 1.45 &392.85 $\pm$ 0.87 \\
nbody\_modified	&637.90 $\pm$ 1.82	&256.78 $\pm$ 0.18	&135.55 $\pm$ 0.33 &103.93 $\pm$ 0.25 \\
pyflate-fast	&3169.35 $\pm$ 1.89	&1278.16 $\pm$ 3.13	&3285.89 $\pm$ 8.51	&1822.36 $\pm$ 11.52 \\
raytrace-simple	&2744.60 $\pm$ 51.72	&1072.66 $\pm$ 1.08	&2778.27 $\pm$ 15.13	&647.24 $\pm$ 5.44 \\
richards	&354.06 $\pm$ 1.00	&63.48 $\pm$ 0.15	&383.93 $\pm$ 3.28 &88.32 $\pm$ 0.91 \\
spambayes	&299.16 $\pm$ 0.35	&338.68 $\pm$ 3.14	&580.90 $\pm$ 24.68 &397.37 $\pm$ 10.60 \\
spectral-norm	&478.63 $\pm$ 0.80	&139.83 $\pm$ 1.54	&353.51 $\pm$ 1.39 &112.10 $\pm$ 1.17 \\
telco	&1207.67 $\pm$ 2.03	&730.00 $\pm$ 2.66	&1296.08 $\pm$ 4.37 &495.23 $\pm$ 2.14 \\
twisted\_names	&9.58 $\pm$ 0.01	&10.43 $\pm$ 0.01	&17.99 $\pm$ 0.27	&7.13 $\pm$ 0.09 \\
\hline
\end{tabular}
\end{center}
\caption{Benchmark Times in Milliseconds}
\label{fig:times}
\end{figure*}
